### 2021-05-14 docs/manuscript/PLOS-MSc-Thesis.tex

The set of interaction values was represented as adjacency matrices $W \in
\mathbb{R}^{3\times4}$ where $i$ represents a regulated node of the GRN and $j$
represents a regulator node of the GRN (Fig \ref{fig:model}A and
\ref{fig:model}B) with $w_{\textit{ij}}~\in [-10,\ 10]$. Values in these
matrices can be negative, zero or positive and represent represion, no
interaction, or activation respectively. The magnitude of the value is
proportional to the strength of the interaction.\\

@@

In order to classify each topology by its subgraph composition, we first created
a matrix  $T = (t_{ij})$ with 714 rows corresponding to each different topology
and 17 columns corresponding to subgraphs shown in \nameref{S4_Fig}.
Each element $t_{ij}$ of
the matrix was 1 if the \emph{j}-th subgraph was present in the \emph{i}-th
topology or 0 if the subgraph was not present.\\

>>>>

The set of interaction values was represented as adjacency matrices $W \in
\mathbb{R}^{3\times4}$ where $i$ represents a regulated node of the GRN and $j$
represents a regulator node of the GRN (Fig \ref{fig:model}A and
\ref{fig:model}B) with $w_{\textit{ij}}~\in [-10,\ 10]$. Values in these
matrices can be negative, zero or positive and represent represion, no
interaction, or activation respectively. The magnitude of the value is
proportional to the strength of the interaction. \hil{In this study we define
a 'genotype' as the set of interaction, diffusion and degradation values that
represent a GRN.}\\

@@

In order to classify each topology by its subgraph composition, we first created
a matrix  $T = (t_{ij})$ with each row corresponding to a different topology
and 17 columns corresponding to subgraphs shown in \nameref{S4_Fig}.
Each element $t_{ij}$ of
the matrix was 1 if the \emph{j}-th subgraph was present in the \emph{i}-th
topology or 0 if the subgraph was not present.\\
